CorReg: model-based pretreatment for regression with correlated variables. Application in steel industry

### 2014-04-01 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@473 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@474 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

 	%plan
 	This paper will first present the reduced model and its properties before describing in Section 3 the algorithm used to find the structure.
 	We will then look at some numerical results on simulated (Section 4) and real industrial datasets (Section 5) before concluding and giving some perspectives in the sixth part.

\section{Model to select decorrelated covariates}
\subsection{The decorrelation problem in regression}
For a model defined by 
	\begin{equation}
		Y_{|X}=X\beta + \varepsilon
	\end{equation}
	where $X$ is the $n\times p$ matrix of the explicative variables, $Y$ the response vector and $\varepsilon \sim \mathcal{N}(0,\sigma_Y^2I_n)$ with $I_n$ the $n$-sized identity matrix,
	we have the following Ordinary Least Squares (OLS) estimators:
	\begin{equation}
		\hat{\beta}=\left(X'X \right) ^{-1}X'Y
	\end{equation}
	With variance 
	\begin{equation}
		\operatorname{Var}(\hat{\beta})=\sigma_Y^2(X'X)^{-1} \label{eqOLS}
	\end{equation}
	 The Mean Squared Error (MSE) on $\hat{\beta}$ is:
	\begin{eqnarray}
		MSE(\hat{\beta}|\beta,X)&=&Bias^2+\operatorname{Tr}(\operatorname{Var}(\hat{\beta})) \\
			&=&0+\sigma_Y^2 \operatorname{Tr}((X'X)^{-1})
	\end{eqnarray}	 
	and when correlations between covariates are strong, the matrix to invert is ill-conditioned, the variance explodes and so does the MSE.
\subsection{Modelisation of the correlations}
Let now $X \in \mathcal{R}^{n\times p}$ be a set of $p$ correlated covariates.
We propose to explicitly define a family of $p_2$ internal regressions between covariates whith $I_2$ the set of indices of endogenous variables in $X$ (explained ones) and $I_1=\{I_1^1,\dots,I_1^p \}$ the set of the sets of indices of exogenous covariates (explaining ones) with $\forall j \notin I_2, I_1^j=\emptyset$. Then we have an explicit structure $S=(I_1,I_2,p_1,p_2)$ where $p_1=(p_1^1,\dots,p_1^{p_2})$ is the vector of the number of covariates in each internal regression. Thus we have $p_2=| I_2|$ and $p_1^j=|I_1^j|$ where $|.|$ represents the cardinal of an ensemble.

@@

\section{Numerical results on simulated datasets}
	\subsection{The datasets}	
	Now we have defined the model and the way to obtain it, we can have a look on some numerical results to see if \textsc{CorReg} 	keeps its promises.
	The \textsc{CorReg} package has been tested on simulated datasets. 
Section \ref{compZ} shows the results obtained in terms of $\hat{S}$. Sections \ref{tableMSEsimtout} and \ref{tableMSEsimgauche} show the results obtained using only \textsc{CorReg}, or \textsc{CorReg} combined with other methods. Tables give both mean and standard deviation of the observed Mean Squared Errors (MSE) on a validation sample of $1 000$ individuals. For each simulation,  $p=40$, $\sigma_Y=10$, $\sigma=0.001$, variables $X_1$ follow Gaussian mixture models of $\lambda=5$ classes which means follow Poisson's law of parameter $\lambda$ and which standard deviation also is $\lambda$. The $B_1^j$ and $\beta_j$ are generated according to the same Poisson law but with a random sign. $S$ only contains binary relationships but \textsc{CorReg} was only constrained to $\max (\hat{p}_1^j)=5$.  
	We used \textsc{Rmixmod} to estimate the densities of each covariate. For each configuration, the walk was launched on $20$ initial structures with a maximum of 9 000 steps each time.

@@

	\clearpage	
\section{Numerical results on real datasets}
\subsection{Quality case study} \label{sectionexfos}
This work takes place in steel industry context, with quality oriented objective : to understand and prevent quality problems on finished product, knowing the whole process.

>>>>

 	%plan
 	This paper will first present the reduced model and its properties before describing in Section 3 the algorithm used to find the structure.
 	We will then look at some numerical results on simulated (Section \ref{sectionsimul}) and real industrial datasets (Section \ref{sectionrealcase}) before concluding and giving some perspectives in the last part.

\section{Model to select decorrelated covariates}
\subsection{The decorrelation problem in regression}
For a model defined by 
	\begin{equation}
		Y_{|X}=X\beta + \varepsilon
	\end{equation}
	where $X$ is the $n\times p$ matrix of the explicative variables, $Y$ the response vector and $\varepsilon \sim \mathcal{N}(0,\sigma_Y^2I_n)$ with $I_n$ the $n$-sized identity matrix,
	we have the following Ordinary Least Squares (OLS) estimators:
	\begin{equation}
		\hat{\beta}=\left(X'X \right) ^{-1}X'Y
	\end{equation}
	With variance 
	\begin{equation}
		\operatorname{Var}(\hat{\beta})=\sigma_Y^2(X'X)^{-1} \label{eqOLS}
	\end{equation}
	 The Mean Squared Error (MSE) on $\hat{\beta}$ is:
	\begin{eqnarray}
		MSE(\hat{\beta}|\beta,X)&=&Bias^2+\operatorname{Tr}(\operatorname{Var}(\hat{\beta})) \\
			&=&0+\sigma_Y^2 \operatorname{Tr}((X'X)^{-1})
	\end{eqnarray}	 
	and when correlations between covariates are strong, the matrix to invert is ill-conditioned, the variance explodes and so does the MSE.
	Another problem is that matricial inversion requires $n\geq p$. When it is not the case, a frequently used alternative is the Moore-Penrose generalized inverse \cite{katsikis2008fast}. In the followings, matrices inverses when $n<p$ will refer to this generalized inverse. Thus OLS can obtain some results even with $n<p$ (see section \ref{sectionsimul} ).
\subsection{Modelisation of the correlations}
Let now $X \in \mathcal{R}^{n\times p}$ be a set of $p$ correlated covariates.
We propose to explicitly define a family of $p_2$ internal regressions between covariates whith $I_2$ the set of indices of endogenous variables in $X$ (explained ones) and $I_1=\{I_1^1,\dots,I_1^p \}$ the set of the sets of indices of exogenous covariates (explaining ones) with $\forall j \notin I_2, I_1^j=\emptyset$. Then we have an explicit structure $S=(I_1,I_2,p_1,p_2)$ where $p_1=(p_1^1,\dots,p_1^{p_2})$ is the vector of the number of covariates in each internal regression. Thus we have $p_2=| I_2|$ and $p_1^j=|I_1^j|$ where $|.|$ represents the cardinal of an ensemble.

@@

\section{Numerical results on simulated datasets} \label{sectionsimul}
	\subsection{The datasets}	
	Now we have defined the model and the way to obtain it, we can have a look on some numerical results to see if \textsc{CorReg} 	keeps its promises.
	The \textsc{CorReg} package has been tested on simulated datasets. 
Section \ref{compZ} shows the results obtained in terms of $\hat{S}$. Sections \ref{tableMSEsimtout} and \ref{tableMSEsimgauche} show the results obtained using only \textsc{CorReg}, or \textsc{CorReg} combined with other methods. Tables give both mean and standard deviation of the observed Mean Squared Errors (MSE) on a validation sample of $1 000$ individuals. For each simulation,  $p=40$, $\sigma_Y=10$, $\sigma=0.001$, variables $X_1$ follow Gaussian mixture models of $\lambda=5$ classes which means follow Poisson's law of parameter $\lambda$ and which standard deviation also is $\lambda$. The $B_1^j$ and $\beta_j$ are generated according to the same Poisson law but with a random sign. $S$ only contains binary relationships but \textsc{CorReg} was only constrained to $\max (\hat{p}_1^j)=5$.  
	We used \textsc{Rmixmod} to estimate the densities of each covariate. For each configuration, the walk was launched on $20$ initial structures with a maximum of 9 000 steps each time.

@@

	\clearpage	
\section{Numerical results on real datasets} \label{sectionrealcase}
\subsection{Quality case study} \label{sectionexfos}
This work takes place in steel industry context, with quality oriented objective : to understand and prevent quality problems on finished product, knowing the whole process.
